---
title: "Workbook"
author: "Julie Kim"
date: "10/6/2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, warning = FALSE, message = FALSE}
library(tidyverse)
#library(plyr)
library(shiny)
library(rsconnect)
library(ggplot2)
#library(ggmap)
#library(maps)
#library(mapdata)
#library(sp)
library(plotly)
#library(scales)
#library(lubridate)
#library(gridExtra)
library(shinydashboard)
```

Questions in Mind
---
+ How do factors change after a drought?
+ What percentage of the population is affected by drought? 
+ Is there a relationship between duration of drought, severity of drought, and contamination levels 
+ Are there certain variables in a population that predict better drought-recovery preparedness? 
+ Example diagrams include: times series plots of water usage, chemical levels etc before, during & after a drought, models to predict how long it takes for... 

Data Loading
---
```{r}
#Load for APP
chemicals = read.csv("chemicals.csv", stringsAsFactors = FALSE)
save.image("draft.RData")
```

```{r}
droughts = read.csv("droughts.csv", stringsAsFactors = FALSE)
occ = read.csv("industry_occupation.csv", stringsAsFactors = FALSE)
edu = read.csv("education_attainment.csv", stringsAsFactors = FALSE)
earnings = read.csv("earnings.csv", stringsAsFactors = FALSE)
water = read.csv("water_usage.csv", stringsAsFactors = FALSE)
droughts_fin = read.csv("drought_clean_final.csv", stringsAsFactors = FALSE)

head(chemicals)
head(droughts)
head(occ)
head(edu)
head(earnings)
```

Data Manipulation on Droughts
---
+ Created a function to determine the length of droughts by measuring droughts spanning consecutive measurement periods of 6 days
```{r}
#Remove all data in `droughts` without drought
droughts = droughts[-which(droughts$none==100),]

#Remove all data in `occ` without population data
occ = occ[which(!is.na(occ$total_employed)),]

#Graph the contamination levels across time for an indicated county 
chem.by.county = function(cty) {
  cty.dat = chemicals[which(chemicals$county == cty),]
  ggplot(cty.dat, aes(x = year, y = value, group = 1)) + 
    geom_line() +
    facet_grid(~ chemical_species)
}

#Remove rows of `edu` and `earnings` that are outside of the timespan of 2012-2016
edu2 = edu[which(edu$year == "2012-2016"),]
earnings2 = earnings[which(earnings$year > 2011),]

```

surface water, ground water

how to minimize the loss in income of industries by changing variables that lead to drought 
self-supplied, import or not

rsconnect::deployApp()

rsconnect::setAccountInfo(name='jupiek',
			  token='8531C52D0ADDBE4AD630C0B828E6B5B4',
			  secret='olTDfyvkdAHjzSgLw+DBk2xUJXHtUG27eyarpoTR')
			  
Necessary data to run app:
chemicals